--- 
title: "Statistical Analysis and Visualizations Using R"
author: "Okan Bulut"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: ["book.bib", "packages.bib"]
biblio-style: "apalike"
link-citations: yes
github-repo: okanbulut/rbook
description: "This book contains the materials for the R course at Techology Training Centre."
---

# Introduction

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.


```{r include=FALSE, eval = TRUE}
# automatically create a bib database for R packages
knitr::write_bib(x = c(.packages(), "bookdown", "knitr", "rmarkdown", "data.table", "sparklyr", "ggplot2", "e1071", "dplyr", "caret", "modelr", "randomForest", "rpart", "rpart.plot", "GGally", "ggExtra", "ggalluvial", "cowplot", "plotly"), file = "packages.bib")
```
